Reproducible Research in R: A tutorial on how to do the same thing more than once

### 2021-08-19 README.Rmd
link preprint
remove table

# A Hitchhiker's Guide to Reproducible Research
<!-- badges: start -->
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)

@@

>>>>

# A Hitchhiker's Guide to Reproducible Research
<!-- badges: start -->

<script type='text/javascript' src='https://d1bxh8uas1mnw7.cloudfront.net/assets/embed.js'></script>

<div data-badge-popover="right" data-badge-type="1" data-doi="10.31234/osf.io/fwxs4" data-hide-no-mentions="true" class="altmetric-embed"></div>

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)

@@

[📃Preprint📃](https://www.doi.org/10.31234/osf.io/fwxs4)
